\thesistitle

### 2019-07-29 sections/clonerefactor.tex
Formula does weird
Fixed compile

\begin{equation}\label{eq:istype3r}
\text{isType3R}(C_1, C_2) = \forall (i_1 \in C_1) \exists (i_2 \in C_2) Fi_1 = Fi_2 \land (gap(i_1, i_2) < gap_threshold \lor gap(i_2, i_1) < gap_threshold)
\end{equation}

Where \textit{F} is the file in which the clone instance is located. \textit{gap_threshold} is the defined threshold percentage of the maximum gap size between two clone instances. \textit{$gap(I_1, I_2)$} is the function that calculates the gap between two clone instances.

>>>>

\begin{equation}\label{eq:istype3r}
\text{isType3R}(C_1, C_2) = \forall (i_1 \in C_1) \exists (i_2 \in C_2) Fi_1 = Fi_2 \land gap(i_1, i_2) < gap\_threshold
\end{equation}

Where \textit{F} is the file in which the clone instance is located. \textit{gap\_threshold} is the defined threshold percentage of the maximum gap size between two clone instances. \textit{$\text{gap}(I_1, I_2)$} is the function that calculates the gap between two clone instances.
